---
title: "R Code + Solution"
author: "Suzlon Energy"
output: 
  html_document:
      number_sections: true
      toc: true
      fig_width: 4.5
      code_folding: hide
      fig_height: 4.5
      theme: cosmo
      highlight: tango
---
Density Plot with Numeric Column
```{r}
i=1
for(i in 1:ncol(w)){
  if( (is.numeric(w[,i]))== FALSE )next
  else{
    plot(density(w[,i]),main=paste("",names(w[i]),"| std:",round(sd(w[,i]),1),"| mean:",round(mean(w[,i]),1),"| media:",round(median(w[,i]),1),"| var:",round(var(w[,i]),1)))
  }
   
}


```

Checking Variance for every Column 
```{r}
var_df1  <- sapply(w[,wnum_df], function(x) var(x,na.rm=TRUE))
```


Data table with `Conditional Format +  Download functionality`.
```{r}
DT::datatable(p,
     selection = "single",
     filter = 'bottom',
     extensions = c('Buttons', 'ColReorder', 'FixedHeader', 'Scroller'),
     rownames = FALSE,
     options = list(
       dom = 'Bfrtip',
       searching = T,
       pageLength = 25,
       searchHighlight = TRUE,
       colReorder = TRUE,
       fixedHeader = TRUE,
       filter = 'top',
       buttons = c('copy', 'csv', 'excel', 'print'),
       paging    = TRUE,
       deferRender = TRUE,
       scroller = TRUE,
       scrollX = TRUE,
       scrollY = TRUE
     )
   ) %>%
     formatStyle(-c(1),
                 color = styleInterval(0, c('red','green'))
                 #backgroundColor = styleInterval(3.4, c('yellow', 'gray'))
     )
```



Heat map using High charter package
```{r}
p <- as.matrix(p)
hchart(p,"heatmap")
```

Bar plot using rAmCharts
```{r}
library(rAmCharts);library(ggplot2)
amBarplot(x = "Column", y = "Comp.1", data = p,
                labelRotation = -45,show_values=TRUE, main = "Variable Importance Score-1")
amBarplot(x = "Column", y = "Comp.2", data = p,
                labelRotation = -45,show_values=TRUE, main = "Variable Importance Score-2")
```

Here Column is `Categorical Column` & `Comp.1` is numeric column. 



Excluding COlumn by names
```{r}
names(wnum_df[,-which(names(wnum_df) %in% names(IQR_df))])
```


Scatter plot with category : High charter
```{r}
library(highcharter)
hchart(final_classified, "scatter", hcaes(x = pc.comp1, y = pc.comp2,group=Cluster))
```

Scatter plot with category : Plotly
```{r}
library(plotly)
plot_ly(data = final_classified, x = ~pc.comp1, y = ~pc.comp2,color=~as.factor(Cluster))%>%
  add_markers(text=final_classified$Turbine, showlegend = TRUE)
```



3D plot in potly
```{r}
plot_ly(data = ts, x = ~tsne_y1, y = ~tsne_y2,z=~tsne_y3,color=~as.factor(Cluster))%>%
  add_markers(text=ts$Turbine, showlegend = TRUE)
```



Function for Calling PCA + Clustering
```{r}
Call_PCA <-function(predictorX,NOC){
  
  #Creating PCA Object----
  pca <- princomp(predictorX, cor=T) 
  
  
  # Plotting PCA Score----
   pc.comp <- pca$scores
   pc.comp1 <- -1*pc.comp[,1] 
   pc.comp2 <- -1*pc.comp[,2] 

  
  # Identifying Optimium No of Cluster----
  set.seed(123)
  k.max <- 15
  data <- pc.comp
  wss <- sapply(1:k.max, 
                function(k){kmeans(data, k, nstart=50,iter.max = 15 )$tot.withinss})
  
  a=data.frame(Cluster = seq(1:length(wss)),Wss = wss)
  a$diff <- abs(a$Wss - mean(a$Wss))
  
  if(missing(NOC)) {
        NOC <- (which.min(a$diff)-1)
    } else {
        NOC 
      }
  opt=(which.min(a$diff)-1)
  
  scree_plot<- plot(1:k.max, wss,
       type="b", pch = 19, frame = FALSE, 
       xlab="Number of clusters K",
       ylab="Total within-clusters sum of squares")
  abline(v=opt,col = "Red" ,lty= 4)
   


  #Performing Kmeans Clustering ----
  X <- cbind(pc.comp1, pc.comp2)
  cl <- kmeans(X,NOC)
  # cl$cluster
  # plot(pc.comp1, pc.comp2,col=cl$cluster)
  # points(cl$centers, pch=15)
  
  az <- cbind(PC1=pc.comp1,PC2=pc.comp2,cluster =cl$cluster )
  az <- as.data.frame(az)
 #az <- cbind(az,predictorX)
  cluster_visual<- ggplot(az , aes(PC1 , PC2 , colour = as.factor(cluster),fill = as.factor(cluster))) +
    stat_ellipse(geom = "polygon",col="black",alpha = 0.5)+geom_point(shape = 21 , col =     "black")
  
  
return(list(scree_plot,cluster_visual))

  
}
```


Function for Identifying Opitmium K-Clustering
```{r}
kval_optimium <- function(wnum_df){
  library(cluster)
        dfc <- as.data.frame(wnum_df)
    dfc[is.na(dfc)] <- 0
  
    k.max <- 7
    data <- data.frame(scale(dfc))
    sil <- rep(0, k.max)
    # Compute the average silhouette width for 
    # k = 2 to k = 15
    for(i in 2:k.max){
      km.res <- kmeans(data, centers = i, nstart = 25)
      ss <- silhouette(km.res$cluster, dist(data))
      sil[i] <- mean(ss[, 3])
    }
    v = which.max(sil)
    return(v)
  
}
```




naming column name with text as Col with indexing as sequence no
```{r}
names(df) <- paste("col", 1:ncol(df), sep="")
```


Excluding Column by Column name 

```{r}
exclu_Column <- c("Occurence","Missing_Percentage")
wnum_df<- wnum_df[ ,!(colnames(wnum_df) %in% exclu_Column)]
```

Correlation of Fins Column with the other variables of the column.
```{r, fig.height=10, fig.width=17}
library(psych)
pairs.panels(df)
```



```{r}
box(
  tags$b("Rule Description:"),
  tags$li("Rule-1: Data Points Above threshold temperature(Q3:47 DegC)"),
  tags$li("Rule-2: Continous remain incresing(5) Above Set Temprature Threshold(47 DegC)"),
  tags$li("Rule-3: Median + 5 DegC"),
  tags$li("Rule-4: Less then 25 DegC")
)
```

Summarising all column of a dataframe
```{r}
a <- lapply(a , function(x) rbind( mean = mean(x) ,
                                  sd = sd(x) ,
                                  median = median(x) ,
                                  minimum = min(x) ,
                                  maximum = max(x) ,
                                  s.size = length(x) ) )

a <- as.data.frame(a)
a <- data.frame(t(a))
a <- round(a,3)
a$variable <- rownames(a)
a <- a[,c(ncol(a),2:(ncol(a)-1))];rownames(a)<- NULL;a
```


All Column mean by group_by
```{r}
a1 %>% group_by(Cluster) %>% summarise_all(mean)
```


Sequence/indexing within the group_by
```{r}
library(dplyr)
df %>% group_by(personid) %>% mutate(id = row_number())
df %>% group_by(personid) %>% mutate(id = 1:n())
df %>% group_by(personid) %>% mutate(id = seq_len(n()))
df %>% group_by(personid) %>% mutate(id = seq_along(personid))
```



Checking NA In group by fashion using DPLYR Library
```{r}
 sql_df %>% 
      group_by(PlantUnitName) %>%
      select_if(function(x) any(is.na(x)))%>% 
      summarise_all(funs(sum(is.na(.))))%>%
  ungroup()
```


DPLYR
```{r}
set.seed(100)
ds <- data.frame(group=c(rep("a",100), rep("b",100), rep("c",100)), 
                 x=rnorm(n = 300, mean = 3, sd = 2), y=rnorm(n = 300, mean = 2, sd = 2))
ds
```
We firstly transform it into a tbl_df object to achieve a better print method. No changes occur on the input data frame. 

```{r}
ds <- tbl_df(ds)
ds
```

```{r}
# Head of ds
ds %>% do(head(.))
```



```{r}
# Head of ds by group
ds %>% group_by(group) %>% do(head(.))
```

```{r}
# Tail (last 3 obs) of x by group
ds %>% group_by(group) %>% do(out=tail(.$x, 3))
```



```{r}
# Tail (last 3 obs) of x by group
ds %>% group_by(group) %>% do(data.frame(out=tail(.$x, 3)))
```


```{r}
my_fun <- function(x, y){
  res_x = mean(x) + 2
  res_y = mean(y) * 5 
  return(data.frame(res_x, res_y))
}
```

```{r}
# Apply my_fun() function to ds by group
ds %>% group_by(group) %>% do(out=my_fun(x=.$x, y=.$y))
```


Applying function from group by for specific column 
```{r}
# Apply my_fun() function to ds by group
ds %>% group_by(group) %>% do(my_fun(x=.$x, y=.$y))
```

LInk :
http://www.milanor.net/blog/dplyr-do-tips-for-using-and-programming/
http://www.milanor.net/blog/aggregation-dplyr-summarise-summarise_each/


Density Plot prep for visualisation 
```{r}
density_data_prep<- function(s1){
p1 <- s1 %>%
  group_by(Tag,PC1)%>%
  summarise(Freq= n())
p1$Y <- p1$Freq/sum(p1$Freq)
p1$Type <- "PC1"
names(p1) <- c("Tag","X","Freq","Y","Type")
p1 <- p1[,c("Tag","Type","X","Y")]


p2 <- s1 %>%
  group_by(Tag,PC2)%>%
  summarise(Freq= n())
p2$Y <- p2$Freq/sum(p2$Freq)
p2$Type <- "PC2"
names(p2) <- c("Tag","X","Freq","Y","Type")
p2 <- p2[,c("Tag","Type","X","Y")]


p3 <- s1 %>%
  group_by(Tag,PC3)%>%
  summarise(Freq= n())
p3$Y <- p3$Freq/sum(p3$Freq)
p3$Type <- "PC3"
names(p3) <- c("Tag","X","Freq","Y","Type")
p3 <- p3[,c("Tag","Type","X","Y")]



a <- rbind(p1,p2,p3)

return(a)
 }
selwtg %>% group_by(Tag) %>% do(density_data_prep(.))
```

EXAMPLE : Try-catch
```{r}
df <- data.frame(Tag = c(1, 1, 1, 1, 2, 2, 2, 2),
             x = c(9,7,3,2,1,1,1,1),
             y = c(1,2,3,4,1,2,3,4))


###FUNCTION METHOD:01
# FUNCTION WITH CHECKING STD FIRST AND ACCORDINGLY RETURNING THE VALUE
# cor_fun<- function(x,y){
#   if (any(sapply(list(x, y), FUN = sd) == 0)) {
#     return(mean(x))
#   } else {
#     val <- cor(x,y)
#     return(val)
#   }
# }

###FUNCTION METHOD:02
# FUNCTION WITH TRYCATCH 
cor_fun<- function(x,y){
  val <- tryCatch(cor(x, y), error = function(e) e, warning = function(w) w)
  if (any(class(val) %in% c("simpleWarning", "warning"))) {
    return(mean(x))
  } else {
    return(val)
  }
}


df %>%
  group_by(Tag) %>%
  summarise(c = cor_fun(x,y))

```


try-catch [Browse]:for loop check
```{r}
i=1
dv <- data.frame()
for(i in 44: max(df_600$Tag)){
  browser()
 df6 <- subset(df_600 , Tag==i)
 print(colSums(is.na(df6)))
 print(summary(df6))
 print(cor(df6$PC1,df6$PC2))
 print(cor(df6$PC1,df6$PC3))
 print(cor(df6$PC2,df6$PC3))
  c <- data.frame(Cor_PC12 = cor_fun(df6$PC1,df6$PC2),
                 Cor_PC13 =  cor_fun(df6$PC1,df6$PC3),
                 Cor_PC23 =  cor_fun(df6$PC2,df6$PC3))

 # c <- data.frame(Cor_PC12 =  cor(df6$PC1,df6$PC2),
 #                 Cor_PC13 =  cor(df6$PC1,df6$PC3),
 #                 Cor_PC23 =  cor(df6$PC2,df6$PC3))
 cat("LOOP:",i,"\n")
 dv <- rbind(dv , c)


}
```



```{r}
#separate into categorical and numeric predictors
total_num <- cbind(total$set, total[,sapply(total, is.numeric), with = FALSE]) #numeric variables only
```

count NAs in numeric variables
```{r}
natr_num <- data.frame(sapply(total_num, function(y) sum(length(which(is.na(y)))))) #count NAs in numeric variables
```


```{r}
natr_num$var <- rownames(natr_num)
colnames(natr_num) <- c("na_count", "var")
natr_num <- natr_num %>%  #only keep the numeric values that have an NAs count > 1
  dplyr::filter(na_count > 0) %>%
  dplyr::mutate(na_perc = na_count / nrow(total_num)) %>%
  dplyr::arrange(desc(na_count))
natr_num$na_perc <- round(natr_num$na_per, 2)
```



```{r}
x = data.frame(x = c(1, 2, NA, 3), y = c(NA, NA, 4, 5))
```


```{r}
apply(x, 2, function(col)sum(is.na(col))/length(col))
```

For Loop for nested
```{r}
x <- matrix(1:6, 2, 3)

for(i in seq_len(nrow(x))) {
        for(j in seq_len(ncol(x))) {
                print(x[i, j])
        }   
}
```



```{r}
# Group wise summary
az<- sql_df %>%
  split(.$PlantUnitName)%>%
  map(summary)

library(tidyverse)
sql_df_in35dloss %>%
  filter(SGrid == 600)%>%
   select(-c("Local.time","seq"))%>%
  split(.$Tag)%>%
  map(summary)

sd_df <- sql_df_in35dloss %>%
  filter(SGrid == 600)%>%
  select(-c("Local.time","seq"))%>%
  group_by(Tag)%>%
  summarise_all(funs(sd),na.rm=TRUE)%>%
  ungroup()

# counting 
sql_df  %>% 
  select (-c(Local.time,ecode))%>%
    group_by(PlantUnitName) %>%
    mutate(N= n())%>%
    summarise_all(funs(sum(is.na(.))))%>%
    ungroup()
```

do.call(cbind, lapply(conv_10, summary))


Rounding only columns which are numeric
```{r}
result_table <- result_table %>%
                    mutate_if(is.numeric, round, 2)
```


Time series Feature Engineering 
```{r}
sd1 <- df %>%
      group_by(Tag,Year,Month,Day)%>%
      summarise(
        Turbine = unique(Turbine),
        Local.time = unique(Local),
        Temp_sumy1 = as.numeric(summary(Temp)[1]),
        Temp_sumy2 = as.numeric(summary(Temp)[2]),
        Temp_sumy3 = as.numeric(summary(Temp)[3]),
        Temp_sumy4 = as.numeric(summary(Temp)[4]),
        Temp_sumy5 = as.numeric(summary(Temp)[5]),
        Temp_IQR = IQR(Temp),
        Temp_mad = mad(Temp),
        
        
        # Temp_acf = acfresid(Temp),
        # Temp_x_acf1 = acf_features(Temp)[1],
        # Temp_x_acf10 = acf_features(Temp)[2],
        # Temp_diff1_acf1 = acf_features(Temp)[3],
        # Temp_diff1_acf10 = acf_features(Temp)[4],
        # Temp_diff2_acf1 = acf_features(Temp)[5],
        # Temp_diff2_acf10 = acf_features(Temp)[6],
        
        # Temp_x_pacf5 = pacf_features(Temp)[1],
        # Temp_diff1x_pacf5 = pacf_features(Temp)[2],
        # Temp_diff2x_pacf5 = pacf_features(Temp)[3],
        
        # Temp_mean =  mean(Temp ,na.rm=TRUE),
        # Temp_median =  median(Temp ,na.rm=TRUE),
        # Temp_mode = mlv(Temp,method='mfv')[['M']],
        Temp_sd =  sd(Temp ,na.rm=TRUE),
        Temp_var = var(Temp,na.rm=TRUE),
        
        Temp_sk = skewness(Temp)[1],
        Temp_kt = kurtosis(Temp)[1],
        
        Temp_min1 = Temp[as.numeric(inflect(Temp,1)$minima[1])] ,
        Temp_min2 = Temp[as.numeric(inflect(Temp,1)$minima[2])] ,
        Temp_min3 = Temp[as.numeric(inflect(Temp,1)$minima[3])] ,
        Temp_max1 = Temp[sort(inflect(Temp,1)$maxima,decreasing = TRUE)[1]],
        Temp_max2 = Temp[sort(inflect(Temp,1)$maxima,decreasing = TRUE)[2]],
        Temp_max3 = Temp[sort(inflect(Temp,1)$maxima,decreasing = TRUE)[3]],
        Temp_lump = lumpiness(Temp),
        #Temp_entpy = entropy(Temp),# Result is always Na
        Temp_stab = stability(Temp),
        #Temp_Lshift = max_level_shift(Temp),
        #Temp_Vshift = max_var_shift(Temp),
        #Temp_freq = frequency(Temp),
        Temp_cros = crossing_points(Temp),
        Temp_fspot = flat_spots(Temp),
        Temp_hurst = hurst(Temp),
        # Temp_unitrt = unitroot_kpss(Temp),
        # Temp_unitpp = unitroot_pp(Temp),
        # Temp_Arc_stat = as.numeric(arch_stat(Temp)),
        # Temp_holt_alpha = as.numeric(holt_parameters(Temp)),
        # Temp_holt_beta = as.numeric(holt_parameters(Temp)[2]),
        # Temp_holt_acfres = as.numeric(acfresid(Temp)),
        #     Temp_2 = measures(Temp)[1],
        N=n())%>%
      ungroup()
```



Heat Map
```{r}
library(highcharter)
heatmap_matrix <- as.matrix(cor(qa[,2:25]))
hchart(heatmap_matrix, type = "heatmap")
```



Exclude and include columns of data frame
```{r}
Exclude_colname <- c("PQ.Index..WPI.","SAP_LOC","Particle.Category.6","Particle.Category.14","TAN.mgKOH.g","Viscosity.40øC.mm2.s")
include_colname <- setdiff(names(df), Exclude_colname)
df1 <- df[,include_colname]
```


plotting mean (meanplot) as per cluster/category in the data frame
```{r fig.height=12, fig.width=16}
library(gplots)
i=1
for(i in 1:ncol(sig_cluster_df)){
  if(is.numeric(sig_cluster_df[,i])==TRUE){
    par(mfrow=c(2,1))
    plotmeans(sig_cluster_df[,i]~az$cluster, digits=2, ccol="red", mean.labels=T, main=paste("",names(sig_cluster_df)[i]))
    boxplot(sig_cluster_df[,i] ~ cluster, data = sig_cluster_df, outpch = NA,main=paste("",names(sig_cluster_df)[i]))
    stripchart(sig_cluster_df[,i] ~ cluster, data = sig_cluster_df, 
               vertical = TRUE, method = "jitter", 
               pch = 21, col = "maroon", bg = "red", 
               add = TRUE)
       } 
}
```


scaling 
```{r}
scaleContinuous = function(data) {
  binary = apply(data, 2, function(x) {all(x %in% 0:1)}) 
  data[!binary] = scale(data[!binary])
  return(data)
}

scaleContinuous(df)
```





```{r}
for (i in 1:max(ready_df$Tag)){
  
  x <- filter(ready_df,Tag==i)
  plot(as.ts(x[,26]),type="l",col="green",
          #ylim=c(20, 75),
          xlab="Days", ylab="Power",main=paste("",unique(x$Tag)))#de
     lines(x[,4],col="blue")#nde
     #lines(x[,7],col="orange")#delta
     legend("topright", legend=c("pow","ws"),
            col=c("green","blue"), lty=1:3, cex=0.8)
  
}
```



```{r eval=FALSE, include=FALSE}
library(dygraphs);library(xts)
    Plot_line <- function(df,k){
      pl <- df
      pl = subset(pl , Tag == k)
      #name <- file.list[[i]]
      a1<-xts(pl$ubwspeed, as.POSIXlt(pl$Local.time, format='%Y-%m-%d %H:%M:%s')) 
      a2<-xts(pl$bwspeed, as.POSIXlt(pl$Local.time, format='%Y-%m-%d %H:%M:%s')) 
      a3<-xts(pl$apower, as.POSIXlt(pl$Local.time, format='%Y-%m-%d %H:%M:%s')) 
      
      a4<-xts(pl$spower, as.POSIXlt(pl$Local.time, format='%Y-%m-%d %H:%M:%s')) 
      a5<-xts(pl$Ploss, as.POSIXlt(pl$Local.time, format='%Y-%m-%d %H:%M:%s')) 
      
      
      A<-cbind(a1,a2,a3,a4,a5) 
      dygraph(A,group = "paramter", main = "Power generation Analysis")%>% dyRangeSelector()%>% 
        dyOptions(useDataTimezone = TRUE)%>% 
        dySeries("..1", label = "ubwspeed",fillGraph = FALSE,color = "#FF0000", axis = 'y')%>%
        dySeries("..2", label = "bwspeed",fillGraph = FALSE,color = "#00FF00", axis = 'y')%>%
        dySeries("..3", label = "apower",fillGraph = FALSE,color = "#0000FF", axis = 'y2')%>%
        
        dySeries("..4", label = "spower",fillGraph = FALSE,color = "#800000", axis = 'y')%>%
        dySeries("..5", label = "ploss",fillGraph = FALSE,color = "#808000", axis = 'y')%>%
       
        dyAxis("y", label = "Multiple Variables")
    }
   
    Plot_line(de,8)
```


http://sas-and-r.blogspot.com/2010/05/example-737-calculation-of-hotellings.html


```{r}
hotelling = function(y1, y2) {
  # check the appropriate dimension
  k = ncol(y1)
  k2 = ncol(y2)
  if (k2!=k) 
    stop("input matrices must have the same number of columns: y1 has ",
      k, " while y2 has ", k2)
     
  # calculate sample size and observed means
  n1 = nrow(y1)
  n2 = nrow(y2)   
  ybar1= apply(y1, 2, mean); ybar2= apply(y2, 2, mean)
  diffbar = ybar1-ybar2
   
  # calculate the variance of the difference in means
  v = ((n1-1)*var(y1)+ (n2-1)*var(y2)) /(n1+n2-2)
   
  # calculate the test statistic and associated quantities
  t2 = n1*n2*diffbar%*%solve(v)%*%diffbar/(n1+n2)
  f = (n1+n2-k-1)*t2/((n1+n2-2)*k)
  pvalue = 1-pf(f, k, n1+n2-k-1)
   
  # return the list of results
  return(list(pvalue=pvalue, f=f, t2=t2, diff=diffbar))
}
```


```{r}
PCA_Insight <- function(df){
num_col <- names(df[,sapply(df, function(x) (is.numeric(x)))])
cat_col <- setdiff(names(df),num_col)

cat("*****KNOW YOUR DATA*****",
  "\nThere are Total",ncol(df),"Features in Data set",
    "\nWith ",nrow(df),"Observation",
    "\nThere are",length(num_col),"Numerical Columns",
    "\nThere are",length(cat_col),"Categorical Columns in Data Set")
cat("\n-------ALL VARIABLE-------------\n")
names(df)
cat("\n-------NUMERIC VARIABLE----------\n")
print(num_col)
cat("\n-------CATEGORICAL VARIABLE----------\n")
print(cat_col)

scaleContinuous = function(data) {
 data <- data[,sapply(data, function(x) is.numeric(x))]
 data <- as.data.frame(data)
  
  binary = apply(data, 2, function(x) {all(x %in% 0:1)}) 
  data[!binary] = scale(data[!binary])
  return(data)
}
dfx <- as.data.frame(df)
df <- scaleContinuous(df[,num_col])

library(psych)
pairs.panels(df, 
             method = "pearson", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE # show correlation ellipses
             )
pca_fit <- prcomp(df,scale. = TRUE)
pca_var <- pca_fit$sdev^2
pca_var_per <-round(pca_var/sum(pca_var)*100,1)
p1<- barplot(pca_var_per,main = "PCA in %",ylab = "Variation in %",xlab = "Principal component", col="blue")
#mtext(text=pca_var_per-0.01,las=1,side=2,outer=FALSE,at=p1)
pca_score_plot <- as.data.frame(pca_fit$x) 
rownames(pca_score_plot) <- dfx$X
plot(PC1~PC2, xlab = '', ylab = '', main = 'SCORING PLOT', data = pca_score_plot)
with(pca_score_plot, text(PC1~PC2, labels = row.names(pca_score_plot), pos = 4))


plot(as.ts(pca_score_plot$PC1),
     type = "o",
     xlab = "Sequence in Order",
     ylab = "Score-1",
     main = "PC1 in order", col = "dark red")



loading_score <- pca_fit$rotation[,1]
var_score <- abs(loading_score)
loading_score_ranked <- sort(var_score,decreasing = TRUE)
top_10varibale <- names(loading_score_ranked[1:10])
top_10varibale
LifeCycleSavings <- as.data.frame(pca_fit$rotation) 
plot(PC1~PC2, xlab = '', ylab = '', main = 'LOADING PLOT', data = LifeCycleSavings)
with(LifeCycleSavings, text(PC1~PC2, labels = row.names(LifeCycleSavings), pos = 4))

library(highcharter)
heatmap_matrix <- as.matrix(LifeCycleSavings)
hchart(heatmap_matrix,type="heatmap")
}
```

Automatic Row binding Code
```{r}
# SETTING R DIRECTORY & LOADING DATA %%%%%%%%%%%%%%%
rm(list = ls())
library(data.table);library(dplyr);library(modeest);library(readxl);library(stringr);library(stringi)
library(lubridate);library(moments);library(data.table);library(dplyr);library(readxl)
setwd("D:\\Suzlon R&D Projects\\Power Curve Analysis")
getwd()
cat("\n ^^^^^^^^^^^^------^^^^^^^^^^^^\n")
file_list <- list.files("data")
tdata  <- read_excel(paste("data//",file_list[4],sep=""))
names(tdata)[1:26]


# INDEX_DF %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
unique_col <- 25
df <- as.data.frame(tdata)
f <- names(df[,seq(2, ncol(df),(unique_col ))])
   
y=str_replace_all(as.list(f), "\n", " ") 
z=strsplit(y, " ")
s=0
for (i in 1:length(z)){
  s[[i]] <- as.list(z[[i]][2])} #For Only Tag
#s[[i]] <- as.list(paste(z[[i]][5],z[[i]][6]))} # For Tag + Variable name
s <- unlist(s)
index_df = data.frame(Tag = seq(1:length(s)),Turbine = s)   
index_df$Turbine <- gsub("\r","",index_df$Turbine)
index_df
rm(list=setdiff(ls(),c("tdata","index_df"))) 

# ROW BINDING ALL TURBINE DATA -------------
unique_col <- 25
spliz <- paste("c(","TRUE,",paste(rep("FALSE",(unique_col-1)),collapse=","),")")
spliz <- gsub(" ","",spliz)
Raw.data <- as.data.frame(tdata)
temp <- Raw.data[,-c(1)]
lst <- split.default(temp,cumsum(rep(eval(parse(text=spliz)), ncol(temp)/unique_col)))
y <- rbindlist(setNames(lst, seq_along(lst)), idcol = "Tag")
y$Tag <- as.numeric(y$Tag);

names(y)[2:ncol(y)] <- paste("V",seq(1:(ncol(y)-1)),sep = "")

y$Local.time <- rep(Raw.data[,1],max(y$Tag))
sql_data <- as.data.frame(y)
sql_data <- sql_data[,c(ncol(sql_data),1:(ncol(sql_data)-1))]
sql_data$V9 <-NULL # 100% Data Loss
sql_data
rm(list=setdiff(ls(),c("tdata","index_df","sql_data")))
```


For loop for dygraph plotting 
```{r}
plt <- function(x){
library(xts)
don = xts(x = cv[,x], order.by = as.POSIXct(cv$Local_time))
#don <- cbind(don)
#names(don)[1]<- names(cv)[x]
}

res <- lapply(2:(ncol(cv)-1), function(i) dygraph(plt(i), group="temp_rain",main = paste("",dimnames(cv)[[2]][i])))
htmltools::tagList(res)
```



Dygraph Dynamic Column selection and plotting
```{r}
start <- as.POSIXct("2012-01-01")
interval <- 60
end <- start + as.difftime((nrow(data_in)-1), units="days")
Local_time<- seq(from=start, by=interval*60*24, to=end)

cv <- cbind(Local_time,data_in)

idi <- which(colnames(cv)== "V2")
cv1<- cv[,c(1,idi)]

  Plot_line_func <- function(pl){
    a1<-xts(pl[,2], as.POSIXlt(pl$Local_time, format='%Y-%m-%d',tz = "UTC")) 
    # a2<-xts(pl[,4], as.POSIXlt(pl$Local.time, format='%Y-%m-%d %H:%M:%s'))
    # a3<-xts(pl[,5], as.POSIXlt(pl$Local.time, format='%Y-%m-%d %H:%M:%s'))
    # a4<-xts(pl[,6], as.POSIXlt(pl$Local.time, format='%Y-%m-%d %H:%M:%s'))
    # a5<-xts(pl[,7], as.POSIXlt(pl$Local.time, format='%Y-%m-%d %H:%M:%s'))
    # a6<-xts(pl[,8], as.POSIXlt(pl$Local.time, format='%Y-%m-%d %H:%M:%s'))
    A<-cbind(a1)
    A <- as.data.frame(A)
    attributes(A)
    names(A)[1] <- paste("..",1,sep="")
    print(A)
    dygraph(A,group = "medi" ,main = paste(" ",names(cv)[idi]))%>% 
      dyRangeSelector()%>% 
      dyOptions(useDataTimezone = TRUE)%>% 
      dySeries("..1", label = names(cv)[idi],fillGraph = FALSE,color = "red", axis = 'y', strokeWidth = 2, strokePattern = "dashed")%>% 
      # dySeries("..2", label = names(pl[4]),fillGraph = FALSE,color = "#B8860B", axis = 'y')%>% 
      # dySeries("..3", label = names(pl[5]),fillGraph = TRUE,color = "#66CDAA", axis = 'y',pointSize = 3)%>% 
      # dySeries("..4", label = names(pl[6]),fillGraph = TRUE,color = "green", axis = 'y',pointSize = 3)%>% 
      # dySeries("..5", label = names(pl[7]),fillGraph = TRUE,color = "blue", axis = 'y',pointSize = 3)%>% 
      # dySeries("..6", label = names(pl[8]),fillGraph = TRUE,color = "black", axis = 'y',pointSize = 3)%>% 
      dyAxis("y", label = "Multiple Variables")%>% 
      dyRoller(rollPeriod = 0)
    
  }
  Plot_line_func(cv1)
```



Put the name from file in the select input 

```{r}
renderUI({
  file_list <- list.files("Input Files_csv//")
  selectInput("sel_file","", choices = file_list)
 })
actionButton('sel_file_bt',label = 'Upload Selected File For Analysis',
              width='100%')

file_df <- reactive({
  input$sel_file_bt
  isolate({
    # file_list <- list.files("Input Files//")
    #  v  <- fread(paste("Input Files//",file_list[1],sep=""))
  v  <- read.csv(paste("Input Files_csv//",input$sel_file,sep=""))
  v <- v %>%
    mutate_if(is.numeric, round, 2)

  })
  return(v)
})
```




```{r}
f1 <- clean_df %>%
    mutate(
      Day =format(Local.time,"%d"),
      Month = format(Local.time,"%m"),
      Year = format(Local.time,"%Y"),
      Hour = format(Local.time,"%H"),
      Minutes = format(Local.time,"%M"),
      Second = format(Local.time,"%S")) %>%
    arrange(Tag)
de <- f1 %>%
  select(-c(Local.time,Hour,Minutes,Second))%>%
  group_by(Tag,Year,Month,Day)%>% 
  summarise_all(mean)%>%
  ungroup()
de <- as.data.frame(de)
de$Local <- as.POSIXct(with(de, paste(Year, Month, Day,sep="-")), "%Y-%m-%d",tz="UTC")
de$Local <- as.POSIXct(de$Local, "%Y-%m-%d %H:%M:%S",tz = "UTC")
de$Hour1 <- NULL
de$Year <- NULL
de$Month <- NULL
de$Day <- NULL
#de$Local <- as.POSIXct(de$Local, "%Y-%m-%d %H:%M:%S",tz = "UTC")

de <- de %>%
  mutate_if(is.numeric,round,2)
de <- as.data.frame(de)
de <- de[,c(ncol(de),1:(ncol(de)-1))]
Daydata <- as.data.frame(de)
```





Plotly Auto Select visualisation
```{r}
library(plotly)                       
# Example dataframe
foo <-data.frame( mon  = c("Jan", "Feb", "Mar"),
                  var_1 = c(100, 200, 300),
                  var_b = c(80, 250, 280),
                  var_three = c(150, 120,201)
)


#------------------------------------------------------------------------------
# UI 
#------------------------------------------------------------------------------
ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(
      checkboxGroupInput('show_vars', 'Columns in the dataset', names(foo),
                         selected = c('mon', 'var_1')),
      helpText('Select the variables to show in the graph.')
    ),
    mainPanel(
      plotlyOutput("myPlot")
    )
  )
)
#------------------------------------------------------------------------------
# SERVER 
# Need to loop through input$show_vars to show a trace for each one?
#------------------------------------------------------------------------------
server <- function(input, output) {
  # a large table, reative to input$show_vars
  output$uteTable = renderDataTable({
    library(ggplot2)
    ute[, input$show_vars, drop = FALSE]
  })
  
  
  output$myPlot = renderPlotly({
    p<- plot_ly(foo, x = ~mon, y = ~var_1, type = 'scatter', mode = 'lines')
    #p <- plot_ly(x=foo$mon, y=foo$var_1, line = list(shape="linear"))
 
    for (item in input$show_vars) {
      #p <- add_trace(p, x = foo$mon, y = foo[[item]], evaluate = TRUE)
      p <- add_trace(p,x = foo$mon, y = foo[[item]],y = ~V3, name = 'V3', mode = 'markers')
    }
    print(p)
  })
  
  
  

}
shinyApp(ui = ui, server = server)
```





```{r}
library(profvis)
profvis({
  rm(list = ls())
  # Creating Dummy data 
  row_id <- 100
  No_of_level <- 4
  spliz <- paste("c(","TRUE,",paste(rep("FALSE",(row_id-1)),collapse=","),")")
  d <- as.data.frame(matrix(,nrow = row_id*No_of_level ,ncol=2))
  names(d) <- c("Tag","y_pred")
  d$Tag <-  cumsum(rep(eval(parse(text=spliz)),4))
  d$y_pred <- sample(3:4, row_id*No_of_level, rep = TRUE)
  d$y_pred <- paste("L",d$y_pred,sep="")
  #### ------------------------------------
  
  
  v <- do.call(rbind, 
             lapply(split(d, d$Tag), function(s){
               res <- s
               res$R2 <- ifelse(as.character(res$y_pred) == "L3", 1, 0)
               res$seq <- seq_along(1:nrow(res))
               re$Aoc <- (1-(res$R2/res$seq))*100
               res$Aoc1 <- (res$R2/res$seq)
               res
             }))
  
  
  # How to replce Below For Loop codes to lapply and get the result in the variable.     
  # v <- data.frame();i=0
  # for (i in (1:max(d$Tag))){
  #   #i=4
  #   s <- filter(d , Tag == i)
  #   s$y_pred <- as.character(s$y_pred)
  #   temp = 0
  #   for(i in 1:nrow(s))
  #   s$R2[i] <- ifelse(s$y_pred[i] == "L3", temp <- temp + 1, 0)
  #   s$seq <- seq_along(1:nrow(s))
  #   s$Aoc <- (1-(s$R2/s$seq))*100
  #   s$Aoc1 <- (s$R2/s$seq)
  #   v <- rbind(v,s)
  # }
  
})
```



Creting New List of Folder if not available 
```{r}
list_folder <- c("Input Files","Input Files_csv","Output Files","Process Tables","Reference Data","Source Code","www")
for (i in 1: length(list_folder)){
  
  sub_dir <- list_folder[i]  
  output_dir <- file.path(main_dir,sub_dir)
  if(!dir.exists(output_dir)){
    dir.create(output_dir)
    
  }else{
    print("Dir Already exist")
  }  
}
```


Creating data frame of .csv file available in main directory folder
```{r}
Fu  <- as.data.frame(matrix(,ncol=2,nrow = length(file.list) ))
names(Fu) <- c("Sr_No","File_name")
Fu$File_name <- file.list
Fu$Sr_No <- seq(1:length(file.list))
Fu
```


normal or scaling
```{r}
    scaleContinuous = function(data) {
      data <- data[,sapply(data, function(x) is.numeric(x))]
      data <- as.data.frame(data)
      
      binary = apply(data, 2, function(x) {all(x %in% 0:1)}) 
      data[!binary] = scale(data[!binary])
      return(data)
    }
    dx <- as.data.frame(dx)
    dx <- scaleContinuous(dx)
```


Auto Naming
```{r}
# Automatic Replace column name ---
name_sake <- names(sql_data)


name_sake[which(grepl("Local",name_sake))] <- "Local_time"
name_sake[which(grepl("Outdoor Temp Average",name_sake))] <- "outdoor_temp"
name_sake[which(grepl("Wind Speed Average",name_sake))] <- "Wspeed"
name_sake[which(grepl("Oil Sump Temp Average",name_sake))] <- "Oil_sump_temp"
name_sake[which(grepl("Temp HSS DE Average",name_sake))] <- "Temp_hss_de"
name_sake[which(grepl("Temp HSS NDE Average",name_sake))] <- "Temp_hss_nde"
name_sake[which(grepl("Temp IMS DE Average",name_sake))] <- "Temp_ims_de"
name_sake[which(grepl("Temp IMS NDE Average",name_sake))] <- "Temp_ims_nde"
name_sake[which(grepl("Generator Speed Average",name_sake))] <- "Gspeed"
name_sake[which(grepl("Temp Fluid Coupling Average",name_sake))] <- "Temp_fluidcoup"
name_sake[which(grepl("Temp Generator Bearing DE Average",name_sake))] <- "Temp_GB_de"
name_sake[which(grepl("Temp Generator Bearing NDE Average",name_sake))] <- "Temp_GB_nde"
name_sake[which(grepl("Nacelle Temp Average",name_sake))] <- "Temp_nach"
name_sake[which(grepl("Pitch Angle 1 Average",name_sake))] <- "Pa1"
name_sake[which(grepl("Pitch Angle 2 Average",name_sake))] <- "Pa2"
name_sake[which(grepl("Pitch Angle 3 Average",name_sake))] <- "Pa3"
name_sake[which(grepl("Pitch Current 1 Average",name_sake))] <- "Pc1"
name_sake[which(grepl("Pitch Current 2 Average",name_sake))] <- "Pc2"
name_sake[which(grepl("Pitch Current 3 Average",name_sake))] <- "Pc3"
name_sake[which(grepl("Event Code Absolute",name_sake))] <- "Ecode"
name_sake[which(grepl("Seconds Grid Connection",name_sake))] <- "Gconn"
name_sake[which(grepl("Temp Main Bearing Average",name_sake))] <- "Temp_mb"
name_sake[which(grepl("Active Power Average",name_sake))] <- "Apower"
name_sake[which(grepl("Current Asymmetry Average",name_sake))] <- "Casym"
name_sake[which(grepl("Reactive Power Average",name_sake))] <- "Rpower"
name_sake[which(grepl("Rotor Speed Average",name_sake))] <- "Rspeed"
name_sake[which(grepl("Drive Train Vibration Maximum",name_sake))] <- "Dvib_max"

names(sql_data) <- name_sake
```




```{r}
library(rAmCharts)
    data("data_stock_2")
    data_stock_2 <- data_stock_2[1:50, ]
    data_stock_2$ts1low <- data_stock_2$ts1-100
    data_stock_2$ts1up <- data_stock_2$ts1+100
    amTimeSeries(data_stock_2, "date", list(c("ts1low", "ts1", "ts1up"), "ts2"), 
                color = c("red", "blue"), bullet = c("round", "square"))
```



```{r}
Plot_line_func <- function(pl,cv){
     #cv <- "outdoor_temp"
     #pl <- as.data.frame(df)
     idi <- which(colnames(pl) == cv)
     idi1 <- which(colnames(pl) == "Apower")
     idi2 <- which(colnames(pl) == "Rpower")
     st1<- pl[,c(1,idi,idi1,idi2)]
    # st1$Anom_mark <- ifelse(st1$Anom_mark == "Yes",max(st1[,2])+2,"NA")
    # st1$Local_time <- as.POSIXct(as.character(st1$Local_time), format='%Y-%m-%d')
     library(xts);library(dygraphs)
     #pl <- st1
     a1<- xts(st1[,2],order.by = st1[,1]) 
      a2<- xts(st1[,3],order.by = st1[,1]) 
       a3<- xts(st1[,4],order.by = st1[,1]) 

     A<-cbind(a1,a2,a3)
     A <- as.data.frame(A)
     #attributes(A)
      names(A)[1:ncol(A)] <- paste("..",seq(1:ncol(A)),sep = "")
     #print(A)
    dygraph(A,group = "medi" )%>% 
      dyRangeSelector() %>% 
      dyOptions(useDataTimezone = FALSE)%>% 
      dySeries("..1", label = names(pl[idi]),fillGraph = FALSE,color = "blue", axis = 'y') %>%
      dySeries("..2", label = names(pl[idi1]),fillGraph = FALSE,color = "#DC143C", axis = 'y2',strokeWidth = 2,strokePattern = "dashed")%>% 
      dySeries("..3", label = names(pl[idi2]),fillGraph = TRUE,color = "red", axis = 'y',strokeWidth = 2,pointSize = 4)%>% 
      #dySeries("..4", label = names(mv1[idi_4]),fillGraph = TRUE,color = "green", axis = 'y',pointSize = 3)%>% 
      dyAxis("y", label = "Multiple Variables") %>% 
      dyRoller(rollPeriod = 0)
     
   }
 
```




```{r}
Plot_line_func(df,"Oil_sump_temp")
```

Making pie chart
```{r}
plot_piechart <- function(df){
  # Create data for the graph.
sq = as.data.frame(table(df$Activity))
x= sq$Freq
#x <-  as.data.frame(table(Modelling_out$y_pred))$Var1
labels <-  (sq$Var1)
piepercent<- round(100*x/sum(x), 2)
# Plot the chart.
pie(x, labels = paste("",piepercent," %","\n",labels), main = "Percentage Distribution",col = rainbow(length(x)))
# legend("topleft", paste("",labels), cex = 0.8,
#    fill = rainbow(length(x)))
  
}

plot_piechart(df)
```


Correlation Matrix using Highcharter
```{r}
library(highcharter)
heatmap_matrix <- as.matrix(cor(the_data_subset))
    row.names(heatmap_matrix) <- names(the_data_subset)
    hchart(heatmap_matrix, type = "heatmap")
```




```{r}
i=1

for (i in (min(hdata$Tag) : max(hdata$Tag))){
  
  
  
  sw = filter(hdata , Tag == i)
  meds <- table(sw$y_pred,sw$Label)
  meds <- scale(meds, FALSE, colSums(meds)) * 100
  my_bar=barplot( meds,beside=TRUE, col=c("green","skyblue","Yellow","Orange","red"), ylab="Frequency (%)", ylim=c(0,100),border = "white",main =   paste("",i,":",file.list[[i]]), srt=45 )
  
  text(my_bar, (scale(meds, FALSE, colSums(meds)) * 100),  paste("",round(meds, 1),"%",sep="") , cex=1, pos=3,col="red")
  legend("topleft", c("L1","L2","L3","L4","L5"), col=c("green","skyblue","Yellow","Orange","red"), lwd=10)
  

}
```





```{r}
fz1 <- fz %>%
  group_by(Tag)%>%
 mutate(Label = ifelse(Local.time >= max(Local.time)-days(7) , "urgent" ,
           ifelse(Local.time >= max(Local.time)-days(23) & Local.time < max(Local.time)-days(7) , "short" ,
           ifelse(Local.time >= max(Local.time)-days(53) & Local.time < max(Local.time)-days(23),"medium","long")))
   
 )
```

Changing date formate
```{r}
format(strptime(as.character(df_train$Date.of.Birth)[1], format="%d-%m-%y"),"%d-%m-%Y")
```



checking Total no of Unique-id
```{r echo=FALSE}
# Converting all int class column to numerical class
for(i in 1:ncol(df_train)){
    if((is.integer(df_train[,i]) == TRUE)){
    df_train[,i] <- as.numeric(df_train[,i])
    }
}
str(df_train)
```


```{r}
x_var <- !(names(df_train) %in% c("UniqueID","loan_default"))# Features variable
y_var <- (names(df_train) %in% c("loan_default"))# Target variables
i_var <- (names(df_train) %in% c("UniqueID"))# index/id variable
```



Suppress error message in shiny
```{r}
tags$style(type="text/css",
           ".shiny-output-error { visibility: hidden; }",
           ".shiny-output-error:before { visibility: hidden; }"
)
```

